Constructing Sailing Match Race Schedules: Round-Robin Pairing Lists

### 2015-06-22 paper.tex
That's not an i.e.
Apostrophe

Criterion~6 allows us to measure the \emph{balance} of a schedule. Perfect balance would be when a skipper has as many matches in first position in flights as in second position in flights, and so on. For example, if we had 9 skippers, each skipper would have 8 matches and could be in the first, second, third or fourth match of a flight. In perfect balance, each of the 8 skippers would appear twice in each position. Balance is one of our optimization criteria, and we do this unconditionally i.e.\ even when there are more skippers than boats.

@@

\section{Discussion}
It was anticipated that this problem would be easy to model. This naivety was due to the use of the
term ``round-robin'' for these schedules, leading us to believe that we could use some of the models
already in the literature \cite{trick2002,trick2008,henz2004}. This naivety slowly dissolved as
we addressed more and more of the ISAF criteria. A number of models we produced were scrapped due to
misunderstanding about the actual problem, i.e.\ a communication problem between the authors.
Eventually this was resolved by presenting the majority of the criteria as a deterministic finite
automaton. This became our Rosetta Stone, with the surprising benefit that it not only improved the
teams communications, it was also a constraint (the \emph{regular} constraint).

>>>>

Criterion~6 allows us to measure the \emph{balance} of a schedule. Perfect balance would be when a skipper has as many matches in first position in flights as in second position in flights, and so on. For example, if we had 9 skippers, each skipper would have 8 matches and could be in the first, second, third or fourth match of a flight. In perfect balance, each of the 8 skippers would appear twice in each position. Balance is one of our optimization criteria, and we do this unconditionally, even when there are more skippers than boats.

@@

\section{Discussion}
It was anticipated that this problem would be easy to model. This naivety was due to the use of the
term ``round-robin'' for these schedules, leading us to believe that we could use some of the models
already in the literature \cite{trick2002,trick2008,henz2004}. This naivety slowly dissolved as
we addressed more and more of the ISAF criteria. A number of models we produced were scrapped due to
misunderstanding about the actual problem, i.e.\ a communication problem between the authors.
Eventually this was resolved by presenting the majority of the criteria as a deterministic finite
automaton. This became our Rosetta Stone, with the surprising benefit that it not only improved the
team's communications, it was also a constraint (the \emph{regular} constraint).
